Software Citation Principles

### 2016-04-19 sc-principles/software-citation-principles.tex
change in prereq use case text to generalize

All use cases assume the existence of a citable software object, typically created by the authors\slash developers of the software.
Developers can achieve this by, e.g., uploading a software release to Figshare or Zenodo~\cite{github-citable-code-guide} to obtain a DOI.
Necessary metadata should then be included in a \texttt{CITATION} file~\cite{ssi-citation-files} or machine-readable \texttt{CITATION.jsonld} file~\cite{transitive_credit_json-ld}.
When software is not freely available (e.g., commercial software), alternative means may be used to create citable objects via identifiers such as RRIDs, although these topics are discussed more in \S\ref{sec:identification} and \S\ref{sec:access}.

>>>>

All use cases assume the existence of a citable software object, typically created by the authors\slash developers of the software.
Developers can achieve this by, e.g., uploading a software release to Figshare or Zenodo~\cite{github-citable-code-guide} to obtain a DOI.
Necessary metadata should then be included in a \texttt{CITATION} file~\cite{ssi-citation-files} or machine-readable \texttt{CITATION.jsonld} file~\cite{transitive_credit_json-ld}.
When software is not freely available (e.g., commercial software) or when there is no clear identifier
to use, alternative means may be used to create citable objects as discussed in \S\ref{sec:access}.
